Depth and thickness of tectonic tremor in the northeastern Olympic Peninsula

### 2021-11-17 paper/agujournaltemplate.tex
Hopefully last one

For each array, and every 5 km by 5 km grid cell located within 25 km, we analyze the one-minute-long time windows corresponding to all the tremor epicenters located within the grid cell. For each three-component seismic station and each channel, we detrended the data, tapered the first and last 5 seconds with a Hann window, removed the instrument response, bandpass filtered between 2 and 8 Hz, and resampled the data to 20 Hz. All these preprocessing operations were done with the Python package obspy. For each seismic station and each one-minute-long time window, we cross correlated the vertical component with the East-West component and with the North-South component. Then, we stacked the cross correlation functions over all the seismic stations of the array. We call this stack $S_{i j} (\tau)$ for time lag $\tau$, the $i$-th channel ($i$=1 or 2 for the North or East channel) and the $j$-th one-minute-long time window for a given epicenter grid/array pair. At each step of this method we experimented with a linear stack, a $n$th-root stack, and a phase-weighted stack ~\cite{SCH_1997} and found that the phase-weighted stack worked best. So, all the stacks discussed here used the phase-weighted method.  Figure 2 shows an example of the envelopes of $S_{i j} (\tau)$ for the Big Skidder array for the 110 one-minute-long time windows when tremor was detected in the 5 km by 5 km grid cell located 7 kilometers southwest of the array. As the energy of the P-waves is expected to be higher on the vertical component, and the energy of the S-waves to be higher on the horizontal components, we interpret this peak to correspond to the time lag between the arrival of the direct P- and S-waves. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/BS_-05_-05_PWS_PWS_cluster_ccwin.eps}
\caption{Envelopes of the stacked cross-correlation functions ordered by time for the Big Skidder array for the 110 one-minute long time windows when tremor was detected in a 5 km by 5 km grid cell located 7 kilometers southwest of the array. Top shows time windows (black) that fit the stack well. Bottom shows time windows (blue) that do not fit the stack well. Left panel is the cross-correlation of the EW component with the vertical component, and right panel is the cross-correlation of the NS component with the vertical component. The cross-correlation functions have been cut between 2 and 8 seconds to focus on the time lags around the peaks.}
\label{pngfiguresample}
\end{figure}

@@

To improve the signal-to-noise ratio of the peak in the stacked cross-correlation, we divided the one-minute-long time windows into two clusters, the ones that match the stacked cross-correlations well, and the ones that do not. In order to do the clustering, we stacked the stacked cross-correlation functions, $S_{i j} (\tau)$, over all the one-minute-long time windows to obtain $S_i (\tau)$. For each one-minute time window $j$ we cross-correlated $S_i (\tau)$ with $S_{i j} (\tau)$ to obtain $S^c_{i j} (\tau)$. For this cross-correlation, we keep only the values of lag times $\tau$ between one second before and one second after the time of the maximum of the absolute value of the stack $S_i (\tau)$. For each $i$ and $j$ we determine 3 numbers from $S^c_{i j} (\tau)$: its value at zero lag time, its maximum absolute value and the time lag at which it takes its maximum absolute value, and we determine one number from $S_{i j} (\tau)$: the ratio of its maximum absolute value to its rms. We considered lag times $\tau$ from 12 to 14 seconds to compute the value of the rms of the $S_{i j} (\tau)$. Each one-minute-long time window is thus associated with eight values of quality criteria, four for each of the the East and North channels. We then classified each one-minute-long time window into two different clusters, based on the value of these criteria, using a K-means clustering algorithm (function sklearn.cluster.KMeans from the Python library SciKitLearn). The K-means procedure is as follows: We choose to have 2 clusters, then we arbitrarily choose a center for each cluster. We put each one-minute-long time window into the cluster to which it is closest (based on the values of the eight criteria). Once all one-minute-long time windows have been put in a cluster, we recompute the mean of the eight criteria for each cluster, and iterate the procedure until convergence. On average, about 35\% of the time windows fit well with the stack and are kept in the first cluster, while 65\% do not fit well with the stack and are removed. For each cluster, we then stacked the envelopes of the cross-correlation functions over all the one-minute-long time windows belonging to that cluster using a phase-weighted stack. We tried using more than 2 clusters, but it did not improve the final stack of the best cluster. Figure 3 shows the stack of the envelopes of the $S_{i j} (\tau)$ over the time windows $j$ that correspond to cluster 0 (red) and cluster 1 (blue).  The clustering has greatly improved the amplitude of the peak for cluster 1, and made the peak nearly disappear for cluster 0. \\

@@

We considered only the horizontal component with the maximum value of the peak. We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the theoretical time lag if the source of the tremor was located on the plate boundary. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor. We did the same analysis for the eight arrays of the experiment. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/uncertainty_PWS_PWS.eps}
\caption{Map of the uncertainty on the depth of the tremor based on the width of the stack of the envelopes of the cross-correlation functions for arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles).}
\label{pngfiguresample}
\end{figure}

In the following, we kept only the data points for which the maximum amplitude of the stack is higher than 0.05. Figures 6 and 7 show respectively a map and three cross-sections of the depth of the source of the tremor. Figure 8 shows a map of the distance between the source of the tremor and the plate boundary from the Preston model, alongside with the depth of the low-frequency earthquake families observed by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR}. There is a good agreement between the depth of the source of the tremor, the depth of the low-frequency earthquake families, and the depth of the plate boundary. On the cross-section figures, we compare the distance of the source of the tremor to the plate boundary for different locations of the cross-section. We note that the depth of the tremor matches well the depth of the low-frequency earthquakes. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/depth_PWS_PWS.eps}
\caption{Map of the depth of the source of the tremor and of the low-frequency earthquake families (small filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR}. The three black lines indicate the positions of the cross-sections shown in Figure 7. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles)}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=5cm, trim={4.5cm 0.5cm 6cm 0cm},clip, angle=270]{figures/section_strike_PWS_PWS.eps}
\caption{Cross-sections showing depth of the tremor and of the low-frequency earthquake families (small filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR} for cross sections A-A' , B-B', and C-C' shown in Figure 6. The black line corresponds to the plate boundary profile of McCrory (2006) along the southern most black line shown on Figure 6, and the dashed line to the plate boundary profile of Preston (2003). The color bar shows the distance of the tremor and the low-frequency earthquakes along the strike. Only tremor and low-frequency earthquakes less than 10 km away from the profile line are shown. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles).}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/d_to_pb_PWS_PWS_P.eps}
\caption{Map of the distance between the plate boundary (from the Preston model) of the tremor and of the low-frequency earthquake families (filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR}). Tremor located below the plate boundary is blue, and above is red. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles).}
\label{pngfiguresample}
\end{figure}

@@

As proposed by ~\citeA{KAO_2009}, the source of the tremor could be distributed inside a layer that is 15 or more kilometers thick. We have assumed that all the tremor within a given grid cell originate from the same depth, and averaged over all the data to get the tremor depth. However, instead of being located on the same plane near the plate boundary, the tremor may be scattered over a layer surrounding the plate boundary. To compute the thickness of this layer, for each location of the array and the source of the tremor, we computed for each one-minute-long time window for which the cross-correlation function matches well the stacked cross-correlation the time lag between the time corresponding to the maximum absolute value for the cross-correlation function and the time corresponding to the maximum absolute value for the stacked cross-correlation. We thus obtained a distribution of time lags and the corresponding distribution of depths, and we tried to estimate the scale of the interval over which the depths vary. Using the standard deviation could lead to overestimate the width of the interval, and the corresponding thickness of the tremor layer, as the standard deviation is very sensitive to outliers. Instead, we use the Qn estimator of ~\citeA{ROU_1993}, which is a more robust estimator of scale, similar to the median absolute deviation. We then used the scale of the interval over which the tremor depth varies as an estimate of the thickness of the tremor layer (see Figure 11). The average thickness of the tremor zone is about 1.6 km, while nearly all the values of the thickness are less than 3km, which is substantially lower than the depth extent from ~\citeA{KAO_2009}. The smallest values for the thickness are about 0.8-2 kilometers. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/Q_PWS_PWS.eps}
\caption{Map of the thickness of the tremor layer estimated from scatter of individual 1-minute tremor windows. Tremor widths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles).}
\label{pngfiguresample}
\end{figure}

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/error_PWS_PWS.eps}
\caption{Map of the residuals from the linear regression fitting all the depths to a plane. Residuals are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (triangles).}
\label{pngfiguresample}
\end{figure}

In Table 1, we report the values of the median, the median absolute deviation (MAD), and the Qn estimator of scale for the difference between the depth of the tremor and the low-frequency earthquakes and the depth of the plate boundary, for the McCrory model and for the Preston model. Small negative values of the median correspond to tremor and low-frequency earthquakes located a little bit above the plate boundary. The depth range of the tremor is larger than the depth range of the low-frequency earthquakes, but it may be due to the uncertainty on the determination of the tremor depth. The tremor and low-frequency earthquakes are slightly closer to the plate boundary for the Preston model than for the McCrory model. This may be due because the P-wave velocity model of ~\citeA{PRE_2003} was used as the initial velocity model by ~\citeA{MER_2020} to compute the full P- and S-wave velocity model that we use to get tremor depth from S minus P times. The Preston P-wave velocity model was also used by ~\citeA{CHE_2017_JGR} to locate the low-frequency earthquake families. \\

\begin{table}
\caption{Summary of distances to plate boundary}
\centering
\begin{tabular}{l c c c}
\hline
 & Median & MAD & Qn \\ 
\hline
Tremor depth - Preston depth & - 0.207 km & 2.623 km & 1.313 km \\
Tremor depth - McCrory depth & - 0.850 km & 2.429 km & 1.390 km \\
LFE depth - Preston depth & - 0.189 km & 1.312 km & 0.871 km \\
LFE depth - McCrory depth & - 0.495 km & 1.805 km & 0.988 km \\
\hline
\end{tabular}
\end{table}

@@

The results presented here are related to a self-consistent 3-D P-wave velocity model and simultaneously determined plate interface model ~\cite{PRE_2003}. This model was used to determine tremor epicenters ~\cite{GHO_2012} and the LFE locations ~\cite{SWE_2019, CHE_2017_JGR} along with an assumed Vp / Vs ratio of 1.73.  The tremor depths in this study were determined using the 3-D model of ~\citeA{MER_2020}. They used the Preston model as a starting model and used P and S arrival times at source-receiver pairs to constrain the S-wave velocity.

@@

\acknowledgments
The authors would like to thank A. Ghosh for sharing his tremor catalog. This project was funded by NSF grant EAR-1358512. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings used for this analysis can be downloaded from the IRIS website using network code XG, 2009-2011. Most of the figures were done using GMT ~\cite{WES_1991}. The Python scripts used to analyze the data and make the figures can be found on the first author's Github account \url{https://github.com/ArianeDucellier/timelags}.

>>>>

For each array, and every 5 km by 5 km grid cell located within 25 km, we analyze the one-minute-long time windows corresponding to all the tremor epicenters located within the grid cell. For each three-component seismic station and each channel, we detrended the data, tapered the first and last 5 seconds with a Hann window, removed the instrument response, bandpass filtered between 2 and 8 Hz, and resampled the data to 20 Hz. All these preprocessing operations were done with the Python package obspy. For each seismic station and each one-minute-long time window, we cross correlated the vertical component with the East-West component and with the North-South component. Then, we stacked the cross correlation functions over all the seismic stations of the array. We call this stack $S_{i j} (\tau)$ for time lag $\tau$, the $i$-th channel ($i$=1 or 2 for the North or East channel) and the $j$-th one-minute-long time window for a given epicenter grid/array pair. At each step of this method we experimented with a linear stack, a $n$th-root stack, and a phase-weighted stack ~\cite{SCH_1997} and found that the phase-weighted stack worked best. So, all the stacks discussed here used the phase-weighted method.  Figure 2 shows an example of the envelopes of $S_{i j} (\tau)$ for the Big Skidder array for the 110 one-minute-long time windows when tremor was detected in the 5 km by 5 km grid cell located 7 kilometers southwest of the array. For all time windows, there is a primary peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at $\tau = 0 s$ (not shown in the Figure). Additionally, for about 40\% of the time windows, we also see a secondary peak in the envelopes of the cross-correlation $S_{i j} (\tau)$ at about $\tau = 4.5 s$. As the energy of the P-waves is expected to be higher on the vertical component, and the energy of the S-waves to be higher on the horizontal components, we interpret this peak to correspond to the time lag between the arrival of the direct P- and S-waves. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/BS_-05_-05_PWS_PWS_cluster_ccwin.eps}
\caption{Envelopes of the stacked cross-correlation functions for the Big Skidder array for the 110 one-minute long time windows when tremor was detected in a 5 km by 5 km grid cell located 7 kilometers southwest of the array. Top shows time windows (black) that fit the stack well. Bottom shows time windows (blue) that do not fit the stack well. Left panel is the cross-correlation of the EW component with the vertical component, and right panel is the cross-correlation of the NS component with the vertical component. The cross-correlation functions have been cut between 2 and 8 seconds to focus on the time lags around the peaks.}
\label{pngfiguresample}
\end{figure}

@@

To improve the signal-to-noise ratio of the peak in the stacked cross-correlation, we divided the one-minute-long time windows into two clusters, the ones that match the stacked cross-correlations well, and the ones that do not. In order to do the clustering, we stacked the stacked cross-correlation functions, $S_{i j} (\tau)$, over all the one-minute-long time windows to obtain $S_i (\tau)$. For each one-minute time window $j$ we cross-correlated $S_i (\tau)$ with $S_{i j} (\tau)$ to obtain $S^c_{i j} (\tau)$. We only want to verify whether the waveform $S_{i j} (\tau)$ around the secondary peak matches well with the stack $S_i (\tau)$. We thus look for the maximum of the absolute value of the stack $S_i (\tau)$ between one second before and one second after the theoretical time lag between P- and S-wave arrival if the source was on the plate boundary. We call the time lag corresponding to this maximum $\tau_{max}$. Then for the cross-correlation between $S_{i j} (\tau)$ and $S_i (\tau)$, we keep only the values of lag times $\tau$ between one second before and one second after $\tau_{max}$. For each $i$ and $j$ we determine 3 numbers from $S^c_{i j} (\tau)$: its value at zero lag time, its maximum absolute value and the time lag at which it takes its maximum absolute value, and we determine one number from $S_{i j} (\tau)$: the ratio of its maximum absolute value $S_{i j} (\tau_{max})$ to its rms. We considered lag times $\tau$ from 12 to 14 seconds to compute the value of the rms of the $S_{i j} (\tau)$. Each one-minute-long time window is thus associated with eight values of quality criteria, four for each of the the East and North channels. We then classified each one-minute-long time window into two different clusters, based on the value of these criteria, using a K-means clustering algorithm (function sklearn.cluster.KMeans from the Python library SciKitLearn). The K-means procedure is as follows: We choose to have 2 clusters, then we arbitrarily choose a center for each cluster. We put each one-minute-long time window into the cluster to which it is closest (based on the values of the eight criteria). Once all one-minute-long time windows have been put in a cluster, we recompute the mean of the eight criteria for each cluster, and iterate the procedure until convergence. On average, about 35\% of the time windows fit well with the stack and are kept in the first cluster, while 65\% do not fit well with the stack and are removed. For each cluster, we then stacked the envelopes of the cross-correlation functions over all the one-minute-long time windows belonging to that cluster using a phase-weighted stack. We tried using more than 2 clusters, but it did not improve the final stack of the best cluster. Figure 3 shows the stack of the envelopes of the $S_{i j} (\tau)$ over the time windows $j$ that correspond to cluster 0 (red) and cluster 1 (blue).  The clustering has greatly improved the amplitude of the peak for cluster 1, and made the peak nearly disappear for cluster 0. \\

@@

To compute the depth, we select the EW or the NS component with the larger maximum value of the peak. We focus on the part of the stack of the envelopes of the cross-correlation functions located between 2 seconds before and 2 seconds after the time lag $\tau_{max}$ corresponding to the secondary peak obtained earlier. We computed the moment centroid of this part of the stack and assumed that it was equal to the time lag between the arrivals of the direct P-wave and the direct S-wave. We then computed the corresponding depth of the source of the tremor for all the locations of the source of the tremor.To verify the effect of the width of the time window for which we compute the moment centroid, we compute the centroid and the corresponding depth of the source for widths equal to 2 seconds, 4 seconds, and 6 seconds. We compute the variations in depths when decreasing the width from 4 seconds to 2 seconds. 87\% of the differences in depth are under 2 kilometers. The median difference is 0.064 km, so there is no bias towards shallower or deeper depths when we decrease the width of the time window. When we compute the variations in depths when increasing the width from 4 seconds to 6 seconds, 84\% of the differences in depth are under 2 kilometers and the median difference is 0.054 km. We did the same analysis for the eight arrays of the experiment and each of the tremor-location grid points. The corresponding stacks of the envelopes are shown in Figures S1 to S7 in the supplementary material. For the two arrays Cat Lake and Lost Cause, there are very few source-array locations that have both enough tremor and a high ratio between the peak and the root mean square. Moreover, for the locations where we have a peak, the peak is often not very clear and stretched along the time axis. We did not use data from these two arrays. For the Port Angeles array, there is only a clear peak for a near vertical incidence of the seismic waves. We choose to keep this array in the analysis in order to have two additional data points in the westernmost region of the study area. \\

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/uncertainty_PWS_PWS.eps}
\caption{Map of the uncertainty on the depth of the tremor based on the width of the stack of the envelopes of the cross-correlation functions for arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons).}
\label{pngfiguresample}
\end{figure}

In the following, we kept only the data points for which the maximum amplitude of the stack is higher than 0.05. Figures 6 and 7 show respectively a map and three cross-sections of the depth of the source of the tremor. Figure 8 shows a map of the distance between the source of the tremor and the plate boundary from the Preston model, alongside with the depth of the low-frequency earthquake families observed by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR,CHE_2017_G3}. There is a good agreement between the depth of the source of the tremor, the depth of the low-frequency earthquake families, and the depth of the plate boundary. On the cross-section figures, we compare the distance of the source of the tremor to the plate boundary for different locations of the cross-section. We note that the depth of the tremor matches well the depth of the low-frequency earthquakes. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/depth_PWS_PWS.eps}
\caption{Map of the depth of the source of the tremor and of the low-frequency earthquake families (small filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR,CHE_2017_G3}. The three black lines indicate the positions of the cross-sections shown in Figure 7. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons)}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=5cm, trim={4.5cm 0.5cm 6cm 0cm},clip, angle=270]{figures/section_strike_PWS_PWS.eps}
\caption{Cross-sections showing depth of the tremor and of the low-frequency earthquake families (small filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR,CHE_2017_G3} for cross sections A-A' , B-B', and C-C' shown in Figure 6. The black line corresponds to the plate boundary profile of ~\citeA{MCC_2006} along the southern most black line shown on Figure 6, and the dashed line to the plate boundary profile of ~\citeA{PRE_2003}. The color bar shows the distance of the tremor and the low-frequency earthquakes along the strike. Only tremor and low-frequency earthquakes less than 10 km away from the profile line are shown. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons).}
\label{pngfiguresample}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/d_to_pb_PWS_PWS_P.eps}
\caption{Map of the distance between the plate boundary (from the Preston model) of the tremor and of the low-frequency earthquake families (filled circles) identified by ~\citeA{SWE_2019} and ~\citeA{CHE_2017_JGR,CHE_2017_G3}). Tremor located below the plate boundary is blue, and above is red. Tremor depths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons).}
\label{pngfiguresample}
\end{figure}

@@

As proposed by ~\citeA{KAO_2009}, the source of the tremor could be distributed inside a layer that is 15 or more kilometers thick. We have assumed that all the tremor within a given grid cell originate from the same depth, and averaged over all the data to get the tremor depth. However, instead of being located on the same plane near the plate boundary, the tremor may be scattered over a layer surrounding the plate boundary. To compute the thickness of this layer, for each location of the array and the source of the tremor, we computed for each one-minute-long time window for which the cross-correlation function matches well the stacked cross-correlation the time lag between the time corresponding to the maximum absolute value for the cross-correlation function and the time corresponding to the maximum absolute value for the stacked cross-correlation. We thus obtained a distribution of time lags and the corresponding distribution of depths, and we tried to estimate the scale of the interval over which the depths vary. An example of time lags distribution is shown in Figure S8 of the supplementary material. Using the standard deviation could lead to overestimate the width of the interval, and the corresponding thickness of the tremor layer, as the standard deviation is very sensitive to outliers. Instead, we use the Qn estimator of ~\citeA{ROU_1993}, which is a more robust estimator of scale, similar to the median absolute deviation (MAD). Qn is equal to the $k$th order statistic of the $\begin{pmatrix} n \\ 2 \end{pmatrix}$ interpoint distances where $n$ is the number of points, and $k = \begin{pmatrix} h \\ 2 \end{pmatrix}$ with $h = \left[ \frac{n}{2} \right] + 1$ and $\left[ x \right]$ denote the integer part of $x$. As the MAD, the Qn estimator is not very sensitive to outliers, and it has the advantage of being suitable for asymmetric distributions, contrary to the MAD, which attaches equal importance to positive and negative deviations from the median. We then used the scale of the interval over which the tremor depth varies as an estimate of the thickness of the tremor layer (see Figure 11). The average thickness of the tremor zone is about 1.6 km, while nearly all the values of the thickness are less than 3km, which is substantially lower than the depth extent from ~\citeA{KAO_2009}. The smallest values for the thickness are about 0.8-2 kilometers. \\

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/Q_PWS_PWS.eps}
\caption{Map of the thickness of the tremor layer estimated from scatter of individual 1-minute tremor windows. Tremor widths are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons).}
\label{pngfiguresample}
\end{figure}

@@

\begin{figure}
\noindent\includegraphics[width=\textwidth, trim={1cm 5cm 3.5cm 4cm},clip]{figures/error_PWS_PWS.eps}
\caption{Map of the residuals from the linear regression fitting all the depths to a plane. Residuals are from arrays Burnt Hill (squares), Big Skidder (stars), Danz Ranch (inverted triangles),  Gold Creek (large circles), Port Angeles (diamonds), and Three Bumps (hexagons).}
\label{pngfiguresample}
\end{figure}

In Table 1, we report the values of the median, the median absolute deviation (MAD), and the Qn estimator of scale for the difference between the depth of the tremor and the low-frequency earthquakes and the depth of the plate boundary, for the McCrory model and for the Preston model. Small negative values of the median correspond to tremor and low-frequency earthquakes located a little bit above the plate boundary. The depth range of the tremor (Qn = 1.3 km) is larger than the depth range of the low-frequency earthquake families from ~\citeA{CHE_2017_JGR,CHE_2017_G3} (Qn = 0.9 km). It is a also larger than the thickness of the flow channel where ~\citeA{SAM_2021} suggest that the LFEs are generated (0.5 to 1.5 km). However, this may be due to the uncertainty on the determination of the tremor depth. The tremor and low-frequency earthquakes are slightly closer to the plate boundary for the Preston model than for the McCrory model. This may be due because the P-wave velocity model of ~\citeA{PRE_2003} was used as the initial velocity model by ~\citeA{MER_2020} to compute the full P- and S-wave velocity model that we use to get tremor depth from S minus P times. The Preston P-wave velocity model was also used by ~\citeA{CHE_2017_JGR,CHE_2017_G3} to locate the low-frequency earthquake families. \\

\begin{table}
\caption{Summary of distances to plate boundary}
\centering
\begin{tabular}{l c c c}
\hline
 & Median & MAD & Qn \\ 
\hline
Tremor depth - Preston depth & - 0.207 km & 2.623 km & 1.313 km \\
Tremor depth - McCrory depth & - 0.850 km & 2.429 km & 1.390 km \\
LFE families depth - Preston depth & - 0.189 km & 1.312 km & 0.871 km \\
LFE families depth - McCrory depth & - 0.495 km & 1.805 km & 0.988 km \\
\hline
\end{tabular}
\end{table}

@@

@@

\acknowledgments
The authors would like to thank A. Ghosh for sharing his tremor catalog. We also would like to thank Charles Sammis and an anonymous reviewer whose reviews have helped improve the paper. This project was funded by NSF grant EAR-1358512. A.D. would like to thank the Integral Environmental Big Data Research Fund from the College of the Environment of University of Washington, which funded cloud computing resources to carry out the data analyses. The seismic recordings used for this analysis can be downloaded from the IRIS website using network code XG, 2009-2011. Most of the figures were done using GMT ~\cite{WES_1991}. The Python scripts used to analyze the data and make the figures can be found on the first author's Github account \url{https://github.com/ArianeDucellier/timelags}.
